shrimp_goby_boatnoise

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
adding knitting setting to cache
test
changing authors

---
title: "shrimp_goby_boatnoise"
author: "Jack Manera"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  cosmo
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
---

>>>>

---
title: "shrimp_goby_boatnoise"
author: "Jack L Manera & Jake M Martin"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  cosmo
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
---

This is a test from the cooding god

```{r setup, include = FALSE}
#kniter setting
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE, # no warnings
cache = TRUE,# Cacheing to save time when kniting
tidy = TRUE
)
```
